
\section{\mysidestyle \textcolor{olgray}{Pre-prints}}
H.~Hu, O.~Sener, F.~Sha, V.~Koltun.
\newblock Drinking from a Firehose: Continual Learning with Web-scale Natural Language. 
\newblock {\em Under Review}.

\section{\mysidestyle \textcolor{olgray}{Peer-Reviewed Publications}}
Z.~Cai, O.~Sener, V.~Koltun.
\newblock Online Continual Learning with Natural Distribution Shifts: An Empirical Study with Visual Data.
\newblock In {\em International Conference on Computer Vision, ICCV 2021}.
\vspace{-2mm}

K.~Gao, O.~Sener.
\newblock Modeling and Optimization Trade-off in Meta-learning. 
\newblock In {\em Neural Information Processing Systems, NeurIPS 2020}.
\vspace{-2mm}

U.~Simsekli, O.~Sener, G.~Deligiannidis, MA.~Erdogdu.
\newblock Hausdorff Dimension, Stochastic Differential Equations, and Generalization in Neural Networks. 
\newblock In {\em Neural Information Processing Systems, NeurIPS 2020}.
\vspace{-2mm}

O.~Sener, V.~Koltun.
\newblock Learning to Guide Random Search. 
\newblock In {\em International Conference on Learning Representations, ICLR 2020}.
\vspace{-2mm}

E.~Gorbunov, A.~Bibi, O.~Sener, H.~Bergou, P.~Richtarik.
\newblock A Stochastic Derivative Free Optimization Method with Momentum. 
\newblock In {\em International Conference on Learning Representations, ICLR 2020}.
\vspace{-2mm}

A.~Bibi, H.~Bergou, O.~Sener, B.~Ghanem, P.~Richtarik.
\newblock A Stochastic Derivative-Free Optimization Method with Importance Sampling: Theory and Learning to Control. 
\newblock In {\em AAAI Conference on Artificial Intelligence, AAAI 2020}.
\vspace{-2mm}

J.~Lambert*, Z.~Liu*, J.~Hays, V.~Koltun.
\newblock MSeg: A Meta-dataset for Multi-domain Semantic Segmentation. 
\newblock In {\em Computer Vision and Pattern Recognition, CVPR 2020}.
\vspace{-2mm}


H.~Wang, S.~Pirk, E.~Yumer, V.~Kim,  O.~Sener, S.~Sridhar, L.~Guibas.
\newblock Learning to Generate Multi-Step Human-Object Interactions from Videos. 
\newblock In {\em Eurographics 2019 (Best Paper Honorable Mention)}.
\vspace{-2mm}

O.~Sener, V.~Koltun.
\newblock Multi-Task Learning as Multi-Objective Optimization. 
\newblock In {\em Neural Information Processing Systems, NeurIPS 2018}.
\vspace{-2mm}

R.~Volpi*, H.~Namkoong*, O.~Sener, J.~Duchi, V.~Murino, S.~Savarese.
\newblock Generalizing to Unseen Domains via Adversarial Data Augmentation. 
\newblock In {\em Neural Information Processing Systems, NeurIPS 2018}.
\vspace{-2mm}

O.~Sener, S.~Savarese.
\newblock Active Learning for Convolutional Neural Networks: A Core-Set Approach.
\newblock In {\em International Conference on Learning Representations, ICLR 2018}.
\vspace{-2mm}

J.~Lambert*, O.~Sener*, S.~Savarese.
\newblock Deep Learning under Privileged Information Using Heteroscedastic Dropout. 
\newblock In {\em Computer Vision and Pattern Recognition, CVPR 2018 (Spotlight Oral)}.
\vspace{-2mm}



 \ifx\academictyperesume\undefined
\else
\newpage
\fi

T.~Standley, O.~Sener, D.~Chen, S.~Savarese.
\newblock Estimating the Mass of an Object from Its Image. 
\newblock In {\em Conference on Robot Learning, CORL 2017}.
\vspace{-2mm}

R.~Luo, O.~Sener, S.~Savarese.
\newblock Scene Semantic Reconstruction from Egocentric RGB-D-Thermal Videos. 
\newblock In {\em 3D Vision, 3DV 2017}.
\vspace{-2mm}

O.~Sener, H.~O. Song, A.~Saxena, S.~Savarese.
\newblock Learning Transferrable Representations for Unsupervised Domain Adaptation. 
\newblock In {\em Neural Information Processing Systems, NeurIPS 2016}.
\vspace{-2mm}

I. ~Armeni, O.~Sener, A.~Zamir, S.~Savarese.
\newblock 3D Semantic Parsing of Large-Scale Indoor Spaces.
\newblock In {\em Computer Vision and Pattern Recognition, CVPR 2016 (Oral)}.
\vspace{-2mm}

O.~Sener, A.~Zamir, S.~Savarese, A.~Saxena.
\newblock Unsupervised Semantic Parsing of Video Collections.
\newblock In {\em International Conference on Computer Vision, ICCV 2015}.
\vspace{-2mm}

O.~Sener, A.~Saxena.
\newblock rCRF: Recursive Estimation of the Beliefs over CRFs for Activity Analysis in RGB-D Videos.
\newblock In {\em Robotics Science and Systems, RSS 2015}.
\vspace{-2mm}


C.~Wu, J.~Zhang, O.~Sener, B.~Selman, S.~Savarese, A.~Saxena
\newblock Watch-n-Patch: Unsupervised Learning of Actions and Relations.
\newblock In {\em Pattern Analysis and Machine Intelligence, IEEE Transactions on}, vol. PP, no. 99, pp.


A.~Saxena, A.~Jain, O.~Sener, A.~Jami, DK.~Misra, HS.~Koppula.
\newblock RoboBrain: Large-Scale Knowledge Engine for Robots.
\newblock In {\em International Symposium on Robotics Research, ISRR 2015}.
\vspace{-2mm}

O.~Sener, K.~Ugur, A.~A. Alatan.
\newblock Efficient MRF Energy Propagation for Video Segmentation via Bilateral Filters.
\newblock In {\em Multimedia, IEEE Transactions on}, vol. 16, no. 5, pp. 1292–1302, Aug 2014.


Y.~Aksoy. O.~Sener, A.~A. Alatan, K.~Ugur.
\newblock Interactive 2d-3d image conversion for mobile devices.
\newblock In {\em IEEE International Conference on Image Processing}, 2012.
\vspace{-2mm}

\ifx\alltyperesume\undefined
\else
\newpage
\fi

O.~Sener, K.~Ugur, A.~A. Alatan.
\newblock Error-tolerant interactive image segmentation using dynamic and iterated graph-cuts.
\newblock In {\em Proceedings of the 2nd international workshop on Interactive multimedia on mobile and portable devices}, ACM Multimedia Workshop.

O.~Sener, K.~Ugur, A.~A. Alatan.
\newblock Robust interactive segmentation via coloring.
\newblock In {\em Proceedings of the 1st International Workshop on Visual
Interfaces for Ground Truth Collection in Computer Vision Applications},
ACM AVI 2012 Workshop.