
\section{\mysidestyle \textcolor{olgray}{Selected Publications}}
Modeling and Optimization Trade-off in Meta-learning.   \hfill {\em NeurIPS 2020} \\
\newblock K.~Gao, O.~Sener. 
\vspace{-2mm}

Hausdorff Dimension, Heavy Tails, and Generalization in Neural Networks. \hfill {\em NeurIPS 2020}\\
\newblock U.~Simsekli, O.~Sener, G.~Deligiannidis, MA.~Erdogdu.
\vspace{-2mm}

Learning to Guide Random Search. \hfill {\em ICLR 2020} \\
\newblock O.~Sener, V.~Koltun.
\vspace{-2mm}

MSeg: A Meta-dataset for Multi-domain Semantic Segmentation. \hfill {\em CVPR 2020}. \\
J.~Lambert, Z.~Liu, O.~Sener, J.~Hays, V.~Koltun.
\vspace{-2mm}

Multi-Task Learning as Multi-Objective Optimization. \hfill {\em NeurIPS 2018} \\
\newblock O.~Sener, V.~Koltun.
\vspace{-2mm}

Generalizing to Unseen Domains via Adversarial Data Augmentation.  \hfill {\em NeurIPS 2018} \\
\newblock R.~Volpi, H.~Namkoong, O.~Sener, J.~Duchi, V.~Murino, S.~Savarese.
\vspace{-2mm}

Active Learning for Convolutional Neural Networks: A Core-Set Approach. \hfill {\em ICLR 2018} \\
\newblock  O.~Sener, S.~Savarese.
\vspace{-2mm}

Deep Learning under Privileged Information Using Heteroscedastic Dropout. \hfill {\em CVPR 2018} \\
\newblock J.~Lambert*, O.~Sener*, S.~Savarese.
\vspace{-2mm}

Learning Transferrable Representations for Unsupervised Domain Adaptation. \hfill {\em NeurIPS 2016} \\
\newblock O.~Sener, H.~O. Song, A.~Saxena, S.~Savarese.
\vspace{-2mm}

3D Semantic Parsing of Large-Scale Indoor Spaces. \hfill {\em CVPR 2016} \\
\newblock I. ~Armeni, O.~Sener, A.~Zamir, S.~Savarese.
\vspace{-2mm}

{\emph{See http://ozansener.net/publications.html for the full list of publications.}}

\iffalse
K.~Gao, O.~Sener.
\newblock Modeling and Optimization Trade-off in Meta-learning. 
\newblock In {\em Neural Information Processing Systems, NeurIPS 2020}.
\vspace{-2mm}


O.~Sener, V.~Koltun.
\newblock Learning to Guide Random Search. 
\newblock In {\em International Conference on Learning Representations, ICLR 2020}.
\vspace{-2mm}

E.~Gorbunov, A.~Bibi, O.~Sener, H.~Bergou, P.~Richtarik.
\newblock A Stochastic Derivative Free Optimization Method with Momentum. 
\newblock In {\em International Conference on Learning Representations, ICLR 2020}.
\vspace{-2mm}


J.~Lambert*, Z.~Liu*, J.~Hays, V.~Koltun.
\newblock MSeg: A Meta-dataset for Multi-domain Semantic Segmentation. 
\newblock In {\em Computer Vision and Pattern Recognition, CVPR 2020}.
\vspace{-2mm}


O.~Sener, V.~Koltun.
\newblock Multi-Task Learning as Multi-Objective Optimization. 
\newblock In {\em Neural Information Processing Systems, NeurIPS 2018}.
\vspace{-2mm}

R.~Volpi*, H.~Namkoong*, O.~Sener, J.~Duchi, V.~Murino, S.~Savarese.
\newblock Generalizing to Unseen Domains via Adversarial Data Augmentation. 
\newblock In {\em Neural Information Processing Systems, NeurIPS 2018}.
\vspace{-2mm}

O.~Sener, S.~Savarese.
\newblock Active Learning for Convolutional Neural Networks: A Core-Set Approach.
\newblock In {\em International Conference on Learning Representations, ICLR 2018}.
\vspace{-2mm}

J.~Lambert*, O.~Sener*, S.~Savarese.
\newblock Deep Learning under Privileged Information Using Heteroscedastic Dropout. 
\newblock In {\em Computer Vision and Pattern Recognition, CVPR 2018 (Spotlight Oral)}.
\vspace{-2mm}


O.~Sener, H.~O. Song, A.~Saxena, S.~Savarese.
\newblock Learning Transferrable Representations for Unsupervised Domain Adaptation. 
\newblock In {\em Neural Information Processing Systems, NeurIPS 2016}.
\vspace{-2mm}

I. ~Armeni, O.~Sener, A.~Zamir, S.~Savarese.
\newblock 3D Semantic Parsing of Large-Scale Indoor Spaces.
\newblock In {\em Computer Vision and Pattern Recognition, CVPR 2016 (Oral)}.
\vspace{-2mm}
\fi