    \textbf{Multimedia Research Group}, METU, Ankara, Turkey \hfill February 2011 \textendash ~August 2013\vspace{0mm}\\\vspace{0mm}
	\hspace{-1mm}Research Assistant  \hfill \vspace{2mm}\\\vspace{0mm}
	\hspace{-1mm}\emph{Worked in collaboration with Nokia Research Center, Tampere.} \\
	Advised by Prof. Ayd\i n Alatan (METU) and Dr. Kemal Ugur (Nokia Research Center, Tampere).

	Developed an efficient interactive video segmentation algorithm via Markov random field energy propagation. Proposed a dynamic method to reuse residual-flows in filtering scenario for time efficiency \emph{(in Transaction on Multimedia 2013)}.

	Developed a method efficiently solving interactive image segmentation problem via dynamic and iterative graph-cuts. Furthermore, improved the robustness of the method via automatic correction of user interaction errors \emph{(in ACM-MM-W 2012, ICIP 2012)}.
	
	Involved in patent application and deployed part of the developed algorithms to production on Nokia N9.

    \textbf{Siemens Corporate Research}, Princeton, NJ \hfill August 2010 \textendash ~February 2011\vspace{0mm}\\\vspace{0mm}
	\hspace{-1mm}Research Intern in Imaging, Analytics and Informatics Department  \hfill \vspace{0mm}\\\vspace{0mm}
	\hspace{-1mm}Advised by Dr. Bogdan Georgescu and Dr. Yang Wang \hfill \vspace{2mm}\\\vspace{0mm}
	\hspace{-1.4mm}Contributed to the development of the LVA(Left Ventricle Anatomy) software. Developed a learning based method for automatic classification of volume contrast echocardiography data.
