
\section{\mysidestyle \textcolor{olgray}{Pre-prints}}

O.~Sener, S.~Savarese.
\newblock A Geometric Approach to Active Learning for Convolutional Neural Networks. 
\newblock In {\em Submission}.
\vspace{-2mm}

H.~Wang, S.~Pirk, O.~Sener, E.~Yumer, V.~Kim, L.~Guibas.
\newblock Learning to Generate Multi-Step Human-Object Interactions from Videos. 
\newblock In {\em Submission}.
\vspace{-2mm}

\newpage

\section{\mysidestyle \textcolor{olgray}{Peer-Reviewed Publications}}

O.~Sener, H.~O. Song, A.~Saxena, S.~Savarese.
\newblock Learning Transferrable Representations for Unsupervised Domain Adaptation. 
\newblock In {\em Neural Information Processing Systems, NIPS 2016}.
\vspace{-2mm}

I. ~Armeni, O.~Sener, A.~Zamir, S.~Savarese.
\newblock 3D Semantic Parsing of Large-Scale Indoor Spaces.
\newblock In {\em Computer Vision and Pattern Recognition, CVPR 2016 (oral)}.
\vspace{-2mm}

O.~Sener, A.~Zamir, S.~Savarese, A.~Saxena.
\newblock Unsupervised Semantic Parsing of Video Collections.
\newblock In {\em International Conference on Computer Vision, ICCV 2015}.
\vspace{-2mm}

O.~Sener, A.~Saxena.
\newblock rCRF: Recursive Estimation of the Beliefs over CRFs for Activity Analysis in RGB-D Videos.
\newblock In {\em Robotics Science and Systems, RSS 2015}.
\vspace{-2mm}


C.~Wu, J.~Zhang, O.~Sener, B.~Selman, S.~Savarese, A.~Saxena
\newblock Watch-n-Patch: Unsupervised Learning of Actions and Relations.
\newblock In {\em Multimedia, IEEE Transactions on}, vol. 16, no. 5, pp. 1292–1302, Aug 2014.


A.~Saxena, A.~Jain, O.~Sener, A.~Jami, DK.~Misra, HS.~Koppula.
\newblock RoboBrain: Large-Scale Knowledge Engine for Robots.
\newblock In {\em International Symposium on Robotics Research, ISRR 2015}.
\vspace{-2mm}

O.~Sener, K.~Ugur, A.~A. Alatan.
\newblock Efficient MRF Energy Propagation for Video Segmentation via Bilateral Filters.
\newblock In {\em Pattern Analysis and Machine Intelligence, IEEE Transactions on}, vol. PP, no. 99, pp.


Y.~Aksoy. O.~Sener, A.~A. Alatan, K.~Ugur.
\newblock Interactive 2d-3d image conversion for mobile devices.
\newblock In {\em IEEE International Conference on Image Processing}, 2012.
\vspace{-2mm}

	O.~Sener, K.~Ugur, A.~A. Alatan.
	\newblock Error-tolerant interactive image segmentation using dynamic and iterated graph-cuts.
	\newblock In {\em Proceedings of the 2nd international workshop on Interactive multimedia on mobile and portable devices}, ACM Multimedia Workshop.
  %  \newpage

    O.~Sener, K.~Ugur, A.~A. Alatan.
	\newblock Robust interactive segmentation via coloring.
	\newblock In {\em Proceedings of the 1st International Workshop on Visual
  	Interfaces for Ground Truth Collection in Computer Vision Applications},
  	ACM AVI 2012 Workshop.

    \section{\mysidestyle \textcolor{olgray}{Patents}}
	A.~Saxena, HS.~Koppula, C.~Wu, and O.~Sener.
	\newblock { Automatically learning and controlling connected devices}.
	\newblock United States Patent Application, 20160248847
	\vspace{-2mm}
	
		K.~Ugur, O.~Sener, E.~Gundogdu, and A.~Alatan.
	\newblock { Interactive Image/Video Segmentation For Mobile 2D/3D Conversion}.
	\newblock International Patent Application, WO 2013144418 A1
	\vspace{-2mm}
